### 2011-09-07 Text/paper.tex
More results. Need to do grid convergence and bubble train.

@@

We perform simulations in the frame moving with the bubble (velocity
$U_{bubble}$), that the bubble position stands steady. The bubble velocity $U_{bubble}$ is
different from the bulk velocity $U_{gas}+U_{liq}$. In this case we need to perform coordinate
change:
\beqal
&x(t)=U_{bubble}t\\
&C(x)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a \frac{x}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
&C(t)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)
\feqal
If the unit volume that we simulate is quite long one can obtain the values of the concentration
in the inlet and outlet as a function of time:
\beqal
&C(U_{bubble}\, t)=C^{*}\Bigl(1-\exp\bigr(-k_L\, a\, t
\frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
&C(U_{bubble}\,t+L_{unit})=C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{
U_{bubble}\,t+L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
&=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\exp\bigl(-k_L a
\frac{L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)
\feqal
Therefore the mass transfer coefficient can be calculated as follows:
\beqal
&-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
&k_L a
=\frac{U_{gas}+U_{liq}}{L_{unit}}\ln\Bigl(\frac{C^{*}-C_{inlet}}{C^{*}-C_{outlet}}
\Bigr)
\feqal 
If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$
then the expression for the volumetric mass transfer coefficitent $k_L a$ can be simplified:
\beq
\vol=\frac{\Delta C}{C^{*}} \frac{U_{gas}+U_{liq}}{L_{unit}},
\feq
where $\Delta C=C_{outlet}-C_{inlet}$. If we go to the continuous formulation by changing $L_{unit}$
to be a continuous coordinate $x$, then the following can be obtained \cite{jos-mass}:
\beq
\Delta C = C^{*} \vol \frac{x}{U_{gas}+U_{liq}}
\label{small:conc:mass:estimation}
\feq

>>>>

\section{Other boundary conditions}
We used the outflow boundary conditions for both boundaries and determined the coefficient
according Eq. \ref{theor:continuous:mass:transfer}. One can see the calculated mass transfer
coefficient in time in Fig. \ref{fig:steady:state:jos}.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state_jos.eps}
\caption{The calculated mass transfer coefficient in time with open boundaries $\partial_x
C_{inlet}=\partial_x C_{outlet}=0$. One can see some negative values for volumetric coefficients.
This situation corresponds to the case, then the inlet concentration is greater than the outlet
$C_{inlet}>C_{outlet}$. This corresponds to smaller capillary numbers due to vortex in front of the
bubble. It is the indication that one needs to take more time steps to wait until the outlet
concentration becomes larger than the inlet, which can take a relatively large time period to
wait. Large numbers of the volumetric mass transfer coefficients means the insuffient number of
the unit volumes simulated, as the large difference in the outlet and inlet numbers means the
deviation from the continuous picture. \label{fig:steady:state:jos} }
\end{figure}

@@

We perform simulations in the frame moving with the bubble (velocity
$U_{bubble}$), that the bubble position stands steady. The bubble velocity $U_{bubble}$ is
different from the bulk velocity $U_{gas}+U_{liq}$. In this case we need to perform coordinate
change:
\beqal
&x(t)=U_{bubble}t\\
&C(x)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a \frac{x}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
&C(t)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)
\feqal
If the unit volume that we simulate is quite long one can obtain the values of the concentration
in the inlet and outlet as a function of time:
\beqal
&C(U_{bubble}\, t)=C^{*}\Bigl(1-\exp\bigr(-k_L\, a\, t
\frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
&C(U_{bubble}\,t+L_{unit})=C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{
U_{bubble}\,t+L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
&=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\exp\bigl(-k_L a
\frac{L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)
\feqal
Therefore the mass transfer coefficient can be calculated as follows:
\begin{equation}
\label{theor:continuous:mass:transfer}
\begin{aligned}
&-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
&k_L a
=\frac{U_{gas}+U_{liq}}{L_{unit}}\ln\Bigl(\frac{C^{*}-C_{inlet}}{C^{*}-C_{outlet}}
\Bigr)
\end{aligned}
\end{equation}
If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$
then the expression for the volumetric mass transfer coefficitent $k_L a$ can be simplified:
\beq
\vol=\frac{\Delta C}{C^{*}} \frac{U_{gas}+U_{liq}}{L_{unit}},
\feq
where $\Delta C=C_{outlet}-C_{inlet}$. If we go to the continuous formulation by changing $L_{unit}$
to be a continuous coordinate $x$, then the following can be obtained \cite{jos-mass}:
\beq
\Delta C = C^{*} \vol \frac{x}{U_{gas}+U_{liq}}
\label{small:conc:mass:estimation}
\feq
